An a/b=1.5 Elliptic Billiard (EB) is shown as well as the 1d-family of 3-periodics (blue). These envelop a confocal caustic (brown). The Excentral Triangle is shown (solid green).

The Feuerbach Circumyperbola is rectangular and passes through X1, X4 and X9 (among many other Triangle Centers) and is centered on X11 [1]. Let F be said hyperbola computed dynamically over the 3-periodic family (blue).  Since over the family X9 is stationary at the EB center [2],  F passes there too. X11 is on the Caustic. Also shown is X1156, the intersection of F and the EB [3]. Surprisingly, the asymptotes of F are always parallel to the EB axes.

The Jerabek Circumhyperbola is rectangular and passes through X1, X3, X4, X6 (among others). Its center is X125 [4]. Let Jexc be the Jerabek Hyperbola of the Excentral Triangle (green). X1,X3,X4,X6,X125 of the Excentral correspond to X4,X40,X1,X9,X100 of the reference triangle, in our case, 3-periodics. Notice its center, X100, is always on the EB. Lile F, the asymptotes of Jexc are parallel to the EB axes.

Let F' (resp. Jexc') be a copy of F (resp. Jexc) translated by X11 (resp. X100), so its center coincides with the EB's. These are shown dashed blue (resp. dashed green). The focal axes and foci (f and f') of both F' and Jexc' are shown as a diagonal through the EB center. Notice X1156=-X100 as it is the reflection of X100 on X9 (at the origin). Therefore Jexc' intersects the EB at X1156. Also, F' and J' are given by x y = k, and x y = k', respectively.

Notice the focal length f of both F and F' is the same, as is f' of Jexc and Jexc'. The foremost property illustrated is that over the 3-periodic family the the ratio f'/f is invariant over the family [3] (see top area of video).

Additionally, when f,f' are maximal, the following has been detected experimentally [3]:

1) Jexc' is tangent to E9 at +/- X100.
2) F' is tangent to the Caustic at +/- X11.
3) k' = a/b.

Soundtrack: Edvard Grieg (Peer Gynt): Suite No.1, Op. 46, Morning Mood.

References:

[1] Feuerbach Hyperbola: https://mathworld.wolfram.com/FeuerbachHyperbola.html
[2] Reznik D., Garcia R., Koiller J., "Can the Elliptic Billiard still surprise us?", Math Intelligencer, vol 42, 2019, https://rdcu.be/b2cg1
[3] Reznik D., Garcia R., Koiller J., "Invariants of Circumconics of 3-Periodics in the Elliptic Billiard", 2020. in preparation
[4] Jerabek Hyperbola: https://mathworld.wolfram.com/JerabekHyperbola.html