Narrated experimentation with the family of N-periodics in an Elliptic BIlliard.

When one considers its "pedal polygons" (defined by dropping perpendiculars from an arbitrary point "m" on the plane to the N-periodic or tangential polygons sides), many wonderful things happen, including invariant area ratios [2,3,4] and products and stationary center of mass [1].

Phenomena are governed by (i) the parity of N: odd, even, multiple of four, etc., (iii) which polygon (N-periodic, outer, inner), and (ii) the position of m on the plane. 

0:00 to 5:00 -- area ratio invariants of N-periodics, and their outer
and inner polygon, some proofs in [2,4]
5:00 to 11:00 -- [new] area ratio invariants to pedal polygons
11:00 to 18:00 -- [new] stationary centers of mass of pedal polygons. related [1]
18:00 to 20:00 -- [new] sum (and sometimes product) of squared altitudes is invariant

Here's a list of the 11 new invariants identified in the video:

1) Pedal polygon from point m to N-periodic

1.1) N=0 (mod 4):Π(mi) if m = 0,f1,f2
1.2) N=2 (mod 4): Π(mi) if m = f1,f2

1.3) odd N: Am.A if m = O
1.4) N=0 (mod 4): Am.A for any m
1.5) N=2 (mod 4): Am/A for any m

2) Pedal polygon from point m to tangential polygon to N-periodic

2.1) all N: Σ(mi')^2 for any m
2.2) N even: Π(mi')=1.0 for m=f1,f2
2.3) additionally N=2 (mod 4): Π(mi') for m=O

2.4) odd N: Am' A' if m=O
2.5) N=0 (mod 4): Am'/A' for any m. Note: w/ N=4, Am'/A'=2 for any a/b and m
2.6) N=2 (mod4): Am'.A' for any m

Recent, related bilbiography:

[1] R. Schwartz, S. Tabachnikov, "Centers of mass of Poncelet polygons, 200 years after", 2016. arXiv:1607.04766
[2] Arseniy Akopyan, Richard Schwartz, Serge Tabachnikov "Billiards in ellipses revisited", 2020. arXiv:2001.02934
[3] Misha Bialy, Serge Tabachnikov , "Dan Reznik's identities and more", 2020. arXiv:2001.08469
[4]  Ana C. Chavez-Caliz, "More about areas and centers of Poncelet polygons", 2020. arXiv:2004.05404
[5] D. Reznik, R. Garcia, and J. Koiller, "Can the Elliptic Billiard Still Surprise Us?", Mathematical Intelligencer, vol 42, 2019. https://rdcu.be/b2cg1