The results listed here appear in [1].

Shown is the poristic triangle family (blue). These are triangles with fixed incircle (inradius r) and circumcircle (circumradius R). Let d be the distance between X1 and X3. For the video, R=1,  r=.3627, d=.5241.

The video shows the following phenomena:

a) The Steiner Deltoid of the Excentral (green) family is a ridigly rotating shape, with fixed internally-tangent circle (9-point circle of the excentrals = circumcircle C of the poristics, purple).

b) The family of Simson Lines (dashed green) of the Excentrals (green) with respect to a point P=X40+2R[cos u, sin u] on its (fixed) circumcircle C' (orange, centered on X40, radius 2R), rotates about a fixed point P'=X3+R[cos u, sin u] on the circumcircle C (purple) of the poristic triangles (blue). I.e., the envelope of said Simson Lines is P', a point! Also note: P, P', X1 are collinear. u is varied, P slides on the C', and P' slides on C.

c) The family of Simson Lines (dashed blue) of the Poristics with respect to a point Q=X3+R[cos u, sin u] on its circumcircle C (purple, centered on X3, radius R), rotates about a fixed point Q', i.e., the envelope of said Simson Lines is is Q', a point! As u is varied, Q slides on the C, and Q' slides along an elipse centered on X1 (dashed black). The dimensions of this ellipse has not yet been derived, and it is a function of r and R.

Postscript: the locus of Q' is the ellipse with semiaxes (R-r,r), centered on X1. [2].

[1] W. Gallatly, "The modern geometry of the triangle", Proprerties 53 e 55 (chapter 4, pages 33 a 36).
[2] Prof. Ronaldo Garcia, Private Communication, June 11, 2020.